\newpage
\TOCadd{Acknowledgements}

\section*{\large Acknowledgements}
\noindent This thesis did not happen by accident, nor by some unique gift I alone have.
I would like to thank of primary importance Dr.\ Falk Herwig and Dr.\ Iris Dillmann.
Without your patience, teaching and supporting me through all my doubts and mistakes, this work would not have happened.
Thank you for all the doors you have opened and the opportunities you have given me.
I would also like to thank Dr.\ Pavel Denissenkov for his constant availability to answer all my programming questions and showing me how to use all the tools I needed to do this work.
I am deeply grateful to have learned from you all.

To my parents, who have always been supportive of me. 
Thank you to my mother who taught me how to critically engage in the world and refuse to take things at face value.
Thank you to my father who taught me what a life long dedication to learning looks like and insisting that I become a doctor of stars.

To Sneha, my companion. Words can't begin to express how grateful I am for your support and love, always being there and excited for every step that I have taken in this journey.
Thank you for the FaceTime calls to wake me up in the morning, and the late night scrolls through Instagram together.
Thank you for the motivation every day to work hard and shoot for the stars.

To Mr. Hordyk who told me I would do great things, Mr. Koiter who taught me physics and sparked my love for it, and Mr. Blyleven who who took me from a student who couldn't program Hello World to helping me land my first programming job, thank you for shaping me to be the scientist I am today.
I still hear your advice to this day, and I am the better for it.

To my friends in Victoria and Vancouver who have been there through the frustrations and the joys.
Thank you Praneet, Maeve, Mallory, Daniel, Bryn, Diego, Dhwani, Layla, Aviv, Ruxin, and Jono. 
Grad school without you all would have been a sad and lonely place.

I acknowledge and respect the Lə\'{k}ʷəŋəŋ\ (Songhees and Xʷsepsəm/Esquimalt) Peoples on whose territory I live and work on, and the Lə\'{k}ʷəŋəŋ\ and \underbar{W}SÁNE\'C Peoples whose historical relationships with the land continue to this day.
\\\\\\
\textit{Well, I am just a humble theologian, and as far as I am concerned the whole of astronomy can be summed up by saying `Twinkle, twinkle little star, how I wonder what you are.'}
\begin{flushright}
- Karl Barth
\end{flushright}
